Synthesis of Linear Functional Programs

### 2021-05-09 article/article.tex
more goals

>>>>

The full and partial synthesis mentioned are closely related, in which the latter is also a complete synthesis, but inserted inside another, bigger, program that makes use the synthetized function.

\mypara{Work Plan}
The end goal is to have a synthetizer capable of taking a type (possibly refined) as input,
and to produce (possibly interactively) a function or more (possibly recursive) with that same type.
Besides the synth, we've already created a parser and a type-checker -- more than good preparation for the
development of the synthetizer, they will be useful to \emph{validate} the functions synthetized, and to implement the
synthesis of partial programs. The implementations are in Haskell, a functional language, since it's easier to reason about inference rules that way.
